An Analysis of Neighborhood Attributes in Chicago using Eigenvector Centrality

### 2018-04-29 paper/paper.tex
add this

\usepackage{amsthm}
\usepackage{blindtext}
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}

@@

\begin{adjustbox}{center}
\begin{tabular}{||c | c c c c c c c c c c c c c c | c||} 
 \hline
 & 2002 & 2003 & 2004 & 2005 & 2006 & 2007 & 2008 & 2009 & 2010 & 2011 & 2012 & 2013 & 2014 & 2015 & \%\\[0.5ex] 
 \hline\hline
The Loop       & 0.958 & 0.952 & 0.954 & 0.939 & 0.947 & 0.955 & 0.947 & 0.960 & 0.961 & 0.962 & 0.962 & 0.964 & 0.962 & 0.964 & +0.60\% \\
Streeterville  & 0.162 & 0.176 & 0.180 & 0.203 & 0.206 & 0.168 & 0.174 & 0.157 & 0.146 & 0.144 & 0.134 & 0.131 & 0.115 & 0.129 & -20.4\% \\
O'Hare Airport & 0.121 & 0.084 & 0.079 & 0.078 & 0.057 & 0.079 & 0.120 & 0.063 & 0.077 & 0.070 & 0.090 & 0.074 & 0.095 & 0.082 & -32.3\% \\
South Loop     & 0.102 & 0.124 & 0.113 & 0.125 & 0.115 & 0.110 & 0.114 & 0.109 & 0.075 & 0.081 & 0.086 & 0.089 & 0.090 & 0.065 & -37.0\% \\
River North    & 0.074 & 0.070 & 0.076 & 0.084 & 0.083 & 0.082 & 0.085 & 0.079 & 0.097 & 0.091 & 0.098 & 0.094 & 0.099 & 0.116 & +56.8\% \\
Bronzeville    & 0.041 & 0.036 & 0.049 & 0.056 & 0.016 & 0.044 & 0.050 & 0.048 & 0.037 & 0.034 & 0.011 & 0.014 & 0.013 & 0.011 & -73.2\% \\
Near North     & 0.074 & 0.098 & 0.085 & 0.101 & 0.098 & 0.091 & 0.088 & 0.088 & 0.085 & 0.086 & 0.073 & 0.070 & 0.073 & 0.074 & +0.00\% \\
West Loop Gate & 0.073 & 0.084 & 0.083 & 0.097 & 0.085 & 0.087 & 0.087 & 0.085 & 0.083 & 0.094 & 0.089 & 0.094 & 0.099 & 0.105 & +43.8\% \\
West Town      & 0.039 & 0.052 & 0.049 & 0.052 & 0.054 & 0.048 & 0.049 & 0.049 & 0.041 & 0.045 & 0.046 & 0.042 & 0.047 & 0.053 & +35.9\% \\
Archer Heights & 0.034 & 0.039 & 0.032 & 0.033 & 0.034 & 0.027 & 0.031 & 0.025 & 0.028 & 0.019 & 0.014 & 0.013 & 0.022 & 0.019 & -44.2\% \\
Hyde Park      & 0.049 & 0.043 & 0.063 & 0.092 & 0.077 & 0.080 & 0.100 & 0.067 & 0.096 & 0.087 & 0.094 & 0.088 & 0.088 & 0.089 & +81.6\% \\
 \hline
 \end{tabular}
\end{adjustbox}
\\

\begin{figure}[H]
    \centering
    \includegraphics[width=0.31\textwidth]{Jobs-S000-2002}
    \includegraphics[width=0.31\textwidth]{Jobs-S000-2008}
    \includegraphics[width=0.31\textwidth]{Jobs-S000-2015}

    \caption{This map shows the eigenvector corresponding to the principle eigenvalue for 2002, 2008, and 2015}
    \label{fig:Jobs-S000-2008}
\end{figure}

As can be seen in the map and table employment is Chicago is highly concentrated in the downtown The Loop neighborhood which consistently is ranked above .95 and dominating the rank of all other neighborhoods.  Other consistently important neighborhoods include include Streeterville which is just north of The Loop as well as O'Hare Airport. Looking at the change in rankings overtime can give us an interesting view of how neighborhoods are becoming more or less important centers of employment over time.  For example, West Loop gate which is the neighborhood just west of the Chicago River has become much more important relative to other neighborhoods.  There have been a number of high tech companies that have opened offices in the West Loop since 2014 such Uber and Google to name a few.\footnote{https://www.builtinchicago.org/2014/09/18/meet-neighbors-4-tech-companies-sign-huge-leases-west-loop}.  Hyde Park has also grown in importance driven by the census blocks that cover the University and Harper Court.\footnote{https://fiftythird.uchicago.edu/category/tags/harper-court-partners} \footnote{this feels anecdotal, bring in the other LEHD employment data, how is this conclusion different from just analyzing the counts?}\\

Another interesting view of the data is to look at the value and location of the second eigenvector of the network over time.  As explained before the second eigenvector will depict a completely orthogonal network compared to the primary eigenvector and can give an idea of how more or less important the primary network is than the next network. One way to think of the second eigenvector would be a completely different "economy" that is somehow separate from the primary "economy" in the city, for example it is common for people to live between these regions with less access to the primary region.  In the graph below I show the value of the second eigenvalue over time which decreases from 0.51 to 0.41 from 2002 to 2015.  This means that compared to the primary network the influence of the secondary network is decreasing.  There could be a few reasons for this, for example the primary network could be increasing in size from outside forces or perhaps people from the secondary network are joining the primary network.  An alternative explanation is that people are leaving the secondary network. TODO: any way to show this?\\
\begin{center}
\begin{tikzpicture}
\begin{axis}[
    title={$\lambda_2$ (Second Eigenvalue over Time)},
    xlabel={Year},
    ylabel={$\lambda_2$},
    xmin=2002, xmax=2015,
    ymin=0, ymax=1,
    xtick={2002, 2004, 2006, 2008, 2010, 2012, 2014},
    ytick={0, 0.5},
    legend pos=north west,
    ymajorgrids=true,
    grid style=dashed,
]

\addplot[
    color=blue,
    mark=square,
    ]
    coordinates {
    (2002, 0.51)
    (2003, 0.45)
    (2004, 0.47)
    (2005, 0.45)
    (2006, 0.43)
    (2007, 0.45)
    (2008, 0.44)
    (2009, 0.42)
    (2010, 0.41)
    (2011, 0.40)
    (2012, 0.41)
    (2013, 0.41)
    (2014, 0.40)
    (2015, 0.41)
    };

@@

Next I will take a look at how the different neighborhoods specialize in different jobs.  Below I map the primary eigenvalue for all job categories, ages, and income levels in three years, 2002, 2008, and 2015.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.31\textwidth]{Jobs-SI001-2015}
    \includegraphics[width=0.31\textwidth]{Jobs-SI002-2015}
    \includegraphics[width=0.31\textwidth]{Jobs-SI003-2015}
    \caption{These maps show the eigenvectors for the three different industry categories: Goods Producing (left), Trade, Transportation, Utilities (center), Other (right) for 2015}
    \label{fig:Jobs-S000-2008}
\end{figure}

This method of centrality importance is clearly able to pull out the different networks of employment in Chicago such as how dispersed the Goods Producing sector is compared to the Trade, Transportation, and Utilities sector which is dominated by O'Hare International Airport.  The Other category is dominated by The Loop area where most of the jobs in the city are located. \\

Lastly I will look at the centrality importance of jobs at different income levels.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.31\textwidth]{Jobs-SE001-2015}
    \includegraphics[width=0.31\textwidth]{Jobs-SE002-2015}
    \includegraphics[width=0.31\textwidth]{Jobs-SE003-2015}
    \caption{These maps show the eigenvectors for the three different salary levels: Under \$1,250 left, \$1,250 - \$3,333 center, Over \$3,333 right for 2015.}
    \label{fig:Jobs-S000-2008}
\end{figure}

Above I used the theory of eigenvector centrality to rank the most important neighborhoods of employment for neighborhoods in Chicago.  This perspective gives us a rich view of the composition of a neighborhood as well as how it changes over time in comparision to other neighborhoods in the city.

\subsection{Centrality for Housing}
Similar to how we calculated centrality for employment we can use the same setup to calculate the centrality for housing, answering the question \textit{What neighborhoods are the most important for housing?}.  We can also break down the neighborhoods by most important for High/Middle/and Low income earners based off of the LEHD Dataset.  The top neighborhoods 10 neighborhoods based on their centrality from 2002 are listed below. \\

\begin{table}[h]\centering
\caption{Top Neighborhoods}\label{thelabel}

\begin{adjustbox}{center}
\begin{tabular}{||c | c c c c c c c c c c c c c | c ||} 
 \hline
 & 2002 & 2003 & 2005 & 2006 & 2007 & 2008 & 2009 & 2010 & 2011 & 2012 & 2013 & 2014 & 2015 & | \%\\[0.5ex] 
 \hline\hline
Logan Square     & 0.303 & 0.307 & 0.296 & 0.287 & 0.207 & 0.296 & 0.201 & 0.313 & 0.316 & 0.323 & 0.333 & 0.340 & 0.322 & 6.271\% \\
West Rogers Park & 0.220 & 0.221 & 0.224 & 0.230 & 0.201 & 0.221 & 0.209 & 0.246 & 0.260 & 0.261 & 0.254 & 0.245 & 0.239 & 8.636\% \\
Gresham          & 0.238 & 0.239 & 0.233 & 0.231 & 0.245 & 0.242 & 0.254 & 0.202 & 0.205 & 0.213 & 0.193 & 0.201 & 0.215 & -9.664\% \\
Portage Park     & 0.188 & 0.185 & 0.181 & 0.182 & 0.214 & 0.191 & 0.220 & 0.201 & 0.203 & 0.190 & 0.198 & 0.188 & 0.189 & 0.532\% \\
Archer Heights   & 0.181 & 0.178 & 0.186 & 0.182 & 0.187 & 0.173 & 0.185 & 0.198 & 0.173 & 0.175 & 0.184 & 0.186 & 0.188 & 3.867\% \\
Little Village   & 0.208 & 0.200 & 0.196 & 0.193 & 0.201 & 0.176 & 0.201 & 0.178 & 0.171 & 0.183 & 0.187 & 0.197 & 0.188 & -9.615\% \\
Albany Park      & 0.189 & 0.195 & 0.179 & 0.172 & 0.144 & 0.181 & 0.133 & 0.186 & 0.198 & 0.201 & 0.193 & 0.183 & 0.179 & -5.291\% \\
Englewood        & 0.247 & 0.244 & 0.236 & 0.239 & 0.258 & 0.223 & 0.252 & 0.197 & 0.185 & 0.178 & 0.172 & 0.177 & 0.179 & -27.530\% \\
Bridgeport       & 0.139 & 0.147 & 0.146 & 0.157 & 0.171 & 0.165 & 0.181 & 0.189 & 0.171 & 0.176 & 0.175 & 0.171 & 0.174 & 25.180\% \\
Rogers Park      & 0.154 & 0.151 & 0.150 & 0.159 & 0.133 & 0.155 & 0.127 & 0.158 & 0.172 & 0.175 & 0.177 & 0.175 & 0.174 & 12.987\% \\ \hline
 \end{tabular}
\end{adjustbox}
\end{table}
\\

Some things to notice right away are that the rankings are much more stable than they were for the employment dataset as most neighborhoods only increasing or decreasing in the single digits over the 14 year timespan.  Also, the distributions of the rankings are a lot more even across neighborhoods compared to the employment dataset which was dominated by The Loop neighborhood. \\

\begin{figure}[H]
    \centering
    \includegraphics[width=1.0\textwidth]{Houses-S000-2015}
    \caption{This map shows the eigenvector that corresponds to the principal eigenvalue for the housing pagerank algorithm.}
    \label{fig:Houses-S000-2015}
\end{figure}

@@

\begin{table}[h]\centering
\caption{Top Neighborhoods for Young Workers (Age < 29)}\label{thelabel}
\begin{adjustbox}{center}
\begin{tabular}{||c | c c c c c c c c c c c c c c | c ||} 
 \hline
 & 2002 & 2003 & 2004 & 2005 & 2006 & 2007 & 2008 & 2009 & 2010 & 2011 & 2012 & 2013 & 2014 & 2015 & | \%\\[0.5ex] 
 \hline\hline
Logan Square     & 0.355 & 0.364 & 0.341 & 0.353 & 0.338 & 0.262 & 0.368 & 0.235 & 0.388 & 0.385 & 0.398 & 0.408 & 0.391 & 0.385 & +8.451\% \\
Little Village   & 0.248 & 0.247 & 0.244 & 0.253 & 0.234 & 0.235 & 0.200 & 0.228 & 0.207 & 0.202 & 0.224 & 0.224 & 0.230 & 0.217 & -12.500\% \\
Gresham          & 0.194 & 0.201 & 0.215 & 0.197 & 0.190 & 0.209 & 0.219 & 0.227 & 0.164 & 0.173 & 0.174 & 0.158 & 0.187 & 0.209 & +7.732\% \\
Englewood        & 0.244 & 0.257 & 0.253 & 0.239 & 0.234 & 0.262 & 0.226 & 0.254 & 0.183 & 0.157 & 0.165 & 0.162 & 0.175 & 0.205 & -15.984\% \\
Archer Heights   & 0.197 & 0.184 & 0.191 & 0.199 & 0.191 & 0.198 & 0.174 & 0.205 & 0.209 & 0.166 & 0.186 & 0.195 & 0.198 & 0.189 & -4.061\% \\
Lake View        & 0.155 & 0.171 & 0.191 & 0.185 & 0.212 & 0.186 & 0.214 & 0.156 & 0.240 & 0.215 & 0.208 & 0.191 & 0.177 & 0.187 & +20.645\% \\
Brighton Park    & 0.187 & 0.189 & 0.182 & 0.186 & 0.189 & 0.145 & 0.158 & 0.145 & 0.156 & 0.164 & 0.159 & 0.183 & 0.170 & 0.179 & -4.278\% \\
West Rogers Park & 0.169 & 0.165 & 0.168 & 0.176 & 0.169 & 0.169 & 0.178 & 0.185 & 0.192 & 0.206 & 0.208 & 0.191 & 0.175 & 0.178 & +5.325\% \\
Rogers Park      & 0.142 & 0.139 & 0.140 & 0.144 & 0.153 & 0.126 & 0.145 & 0.135 & 0.154 & 0.166 & 0.154 & 0.154 & 0.158 & 0.174 & +22.535\% \\
Marquette Park   & 0.140 & 0.144 & 0.150 & 0.176 & 0.180 & 0.164 & 0.151 & 0.160 & 0.131 & 0.132 & 0.135 & 0.124 & 0.142 & 0.167 & +19.286\% \\
Gage Park        & 0.155 & 0.162 & 0.160 & 0.142 & 0.150 & 0.153 & 0.141 & 0.144 & 0.155 & 0.142 & 0.137 & 0.174 & 0.166 & 0.166 & +7.097\% \\
 \hline
 \end{tabular}

@@

\begin{table}[h]\centering
\caption{Top Neighborhoods for Old Workers (Age over 55)}\label{thelabel}
\begin{adjustbox}{center}
\begin{tabular}{||c | c c c c c c c c c c c c c c | c ||} 
 \hline
 & 2002 & 2003 & 2004 & 2005 & 2006 & 2007 & 2008 & 2009 & 2010 & 2011 & 2012 & 2013 & 2014 & 2015 & | \%\\[0.5ex] 
 \hline\hline
West Rogers Park & 0.229 & 0.248 & 0.234 & 0.220 & 0.225 & 0.186 & 0.247 & 0.183 & 0.273 & 0.293 & 0.301 & 0.302 & 0.273 & 0.281 & +22.707\% \\
Logan Square     & 0.231 & 0.224 & 0.223 & 0.201 & 0.211 & 0.129 & 0.196 & 0.167 & 0.234 & 0.225 & 0.240 & 0.246 & 0.265 & 0.239 & +3.463\% \\
Portage Park     & 0.183 & 0.202 & 0.213 & 0.204 & 0.189 & 0.220 & 0.219 & 0.239 & 0.216 & 0.240 & 0.225 & 0.215 & 0.242 & 0.235 & +28.415\% \\
Gresham          & 0.314 & 0.292 & 0.319 & 0.312 & 0.301 & 0.280 & 0.261 & 0.283 & 0.238 & 0.238 & 0.221 & 0.220 & 0.228 & 0.229 & -27.070\% \\
Jefferson Park   & 0.193 & 0.200 & 0.185 & 0.194 & 0.184 & 0.189 & 0.225 & 0.194 & 0.231 & 0.208 & 0.204 & 0.214 & 0.235 & 0.208 & +7.772\% \\
Bridgeport       & 0.119 & 0.139 & 0.148 & 0.134 & 0.151 & 0.189 & 0.170 & 0.190 & 0.200 & 0.185 & 0.191 & 0.209 & 0.197 & 0.194 & +63.025\% \\
Albany Park      & 0.155 & 0.164 & 0.159 & 0.164 & 0.150 & 0.118 & 0.176 & 0.121 & 0.174 & 0.179 & 0.192 & 0.182 & 0.175 & 0.186 & +20.000\% \\
Archer Heights   & 0.159 & 0.156 & 0.155 & 0.181 & 0.173 & 0.178 & 0.168 & 0.167 & 0.194 & 0.160 & 0.163 & 0.172 & 0.158 & 0.168 & +5.660\% \\
Little Village   & 0.150 & 0.154 & 0.164 & 0.162 & 0.169 & 0.181 & 0.150 & 0.196 & 0.155 & 0.145 & 0.167 & 0.163 & 0.171 & 0.161 & +7.333\% \\
West Pullman     & 0.185 & 0.205 & 0.189 & 0.177 & 0.241 & 0.172 & 0.175 & 0.179 & 0.164 & 0.153 & 0.142 & 0.138 & 0.142 & 0.161 & -12.973\% \\
 \hline
 \end{tabular}

>>>>

\usepackage{amsthm}
\usepackage{blindtext}
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\pgfplotsset{compat=1.12}
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}

@@

\begin{table}[h]\centering
\caption{Employment Neighborhood Rank}\label{thelabel}
\begin{adjustbox}{center}
\begin{tabular}{||c | c c c c c c c c c c c c c c | c ||} 
 \hline
 & 2002 & 2003 & 2004 & 2005 & 2006 & 2007 & 2008 & 2009 & 2010 & 2011 & 2012 & 2013 & 2014 & 2015 & \%\\[0.5ex] 
 \hline\hline
The Loop & .958 & .952 & .954 & .939 & .947 & .955 & .947 & .960 & .961 & .962 & .962 & .964 & .962 & .964 & .63\% \\
Streeterville & .162 & .176 & .180 & .203 & .206 & .168 & .174 & .157 & .146 & .144 & .134 & .131 & .115 & .129 & -2.37\% \\
River North & .074 & .070 & .076 & .084 & .083 & .082 & .085 & .079 & .097 & .091 & .098 & .094 & .099 & .116 & 56.76\% \\
West Loop Gate & .073 & .084 & .083 & .097 & .085 & .087 & .087 & .085 & .083 & .094 & .089 & .094 & .099 & .105 & 43.84\% \\
O'Hare & .121 & .084 & .079 & .078 & .057 & .079 & .120 & .063 & .077 & .070 & .090 & .074 & .095 & .082 & -32.23\% \\
Near North & .074 & .098 & .085 & .101 & .098 & .091 & .088 & .088 & .085 & .086 & .073 & .070 & .073 & .074 & .00\% \\
South Loop & .102 & .124 & .113 & .125 & .115 & .110 & .114 & .109 & .075 & .081 & .086 & .089 & .090 & .065 & -36.27\% \\
Hyde Park & .049 & .043 & .063 & .092 & .077 & .080 & .100 & .067 & .096 & .087 & .094 & .088 & .088 & .053 & 8.16\% \\
West Town & .039 & .052 & .049 & .052 & .054 & .048 & .049 & .049 & .041 & .045 & .046 & .042 & .047 & .053 & 35.90\% \\
Near West Side & .033 & .040 & .033 & .039 & .016 & .017 & .040 & .036 & .036 & .038 & .042 & .042 & .042 & .044 & 33.33\% \\ \hline
 \end{tabular}
\end{adjustbox}
\end{table}
\\

\begin{figure}[H]
    \centering
    \includegraphics[width=0.31\textwidth]{Jobs-S000-2002}
    \includegraphics[width=0.31\textwidth]{Jobs-S000-2008}
    \includegraphics[width=0.31\textwidth]{Jobs-S000-2015}
    \caption{This map shows the eigenvector corresponding to the principle eigenvalue for 2002, 2008, and 2015}
    \label{fig:Jobs-S000-2008}
\end{figure}

As can be seen in the map and table employment is Chicago is highly concentrated in the downtown The Loop neighborhood which consistently is ranked above .95 and dominating the rank of all other neighborhoods.  Other consistently important neighborhoods include include Streeterville which is just north of The Loop as well as O'Hare Airport. Looking at the change in rankings overtime can give us an interesting view of how neighborhoods are becoming more or less important centers of employment over time.  For example, West Loop Gate which is the neighborhood just west of the Chicago River has become much more important relative to other neighborhoods.  There have been a number of high tech companies that have opened offices in the West Loop since 2014 such Uber and Google to name a few.\footnote{https://www.builtinchicago.org/2014/09/18/meet-neighbors-4-tech-companies-sign-huge-leases-west-loop}.  Hyde Park has also grown in importance driven by the census blocks that cover the University and Harper Court.\footnote{https://fiftythird.uchicago.edu/category/tags/harper-court-partners} \footnote{this feels anecdotal, bring in the other LEHD employment data, how is this conclusion different from just analyzing the counts?}\\

Another interesting view of the data is to look at the value and location of the second eigenvector of the network over time.  The second eigenvector will depict a completely orthogonal network compared to the primary eigenvector and can give an idea of how more or less important the primary network is than the next network.  One way to think of the second eigenvector would be a completely different ``clique" that is somehow separate from the primary ``clique" in the city.  For example, it is common for people to live between these regions with less access to the primary region.  In the graph below I show the value of the second eigenvalue over time which decreases from 0.51 to 0.41 from 2002 to 2015.  This means that compared to the primary network the influence of the secondary network is decreasing.  There could be a few reasons for this, for example the primary network could be increasing in size, people from the secondary network are joining the primary network, or people are leaving the secondary network.\\
\begin{center}
\begin{tikzpicture}
\begin{axis}[
    title={Second Eigenvalue over Time},
    xlabel={Year},
    ylabel={$\lambda_2$},
    xmin=2002, xmax=2015,
    ymin=0, ymax=1,
    xtick={2002, 2004, 2006, 2008, 2010, 2012, 2014},
    ytick={0, 0.5},
    legend pos=north west,
    ymajorgrids=true,
    grid style=dashed,
    tick label style={/pgf/number format/set thousands separator = {}}
]

\addplot[
    color=blue,
    mark=square,
    ]
    coordinates {
    (2002, 0.51)
    (2003, 0.45)
    (2004, 0.43)
    (2005, 0.40)
    (2006, 0.38)
    (2007, 0.39)
    (2008, 0.42)
    (2009, 0.39)
    (2010, 0.41)
    (2011, 0.40)
    (2012, 0.41)
    (2013, 0.40)
    (2014, 0.39)
    (2015, 0.39)
    };

@@

Next I will take a look at how the different neighborhoods specialize in different job industries.  The eigenvector centrality is able to pull out the different networks of employment in Chicago such as how dispersed the Goods Producing sector is compared to the Trade, Transportation, and Utilities sector which is dominated by O'Hare International Airport.  The Other category is dominated by The Loop area where most of the jobs in the city are located. \\

\begin{figure}[H]
    \centering
    \includegraphics[width=0.31\textwidth]{Jobs-SI001-2015}
    \includegraphics[width=0.31\textwidth]{Jobs-SI002-2015}
    \includegraphics[width=0.31\textwidth]{Jobs-SI003-2015}
    \caption{2015 eigenvectors for the three different industry categories: Goods Producing (left), Trade, Transportation, Utilities (center), Other (right)}
    \label{fig:Jobs-S000-2008}
\end{figure}

Lastly I will look at the eigenvectors across different income levels.  What is interesting about these graphs is how similar the principle eigenvectors are be between income levels.  Even though parts of Chicago are segregated by income level, the importance of each neighborhood for jobs are very similar.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.31\textwidth]{Jobs-SE001-2015}
    \includegraphics[width=0.31\textwidth]{Jobs-SE002-2015}
    \includegraphics[width=0.31\textwidth]{Jobs-SE003-2015}
    \caption{2015 eigenvectors for the three different salary levels: Under \$1,250 left, \$1,250 - \$3,333 center, Over \$3,333 right for 2015.}
    \label{fig:Jobs-S000-2008}
\end{figure}

Above I used the theory of eigenvector centrality to rank the most important neighborhoods of employment for neighborhoods in Chicago.  This perspective gives us a rich view of the composition of a neighborhood as well as how it changes over time in comparison to other neighborhoods in the city.

\subsection{Centrality for Housing}
Similar to how employment centrality was calculated, I calculate housing centrality, answering the question \textit{What neighborhoods are the most important for housing}?  I also break down the neighborhood centrality by most important for High and Low income earners and Old age and Young age based off of the LEHD Dataset.  Below I map the principal eigenvector across the whole population in 2015.  From this map it is apparent the network structure for housing is a lot different than for employment. The distributions of the rankings are a lot more even across neighborhoods compared to the employment dataset which was dominated by The Loop neighborhood.  The top 10 neighborhoods based on their centrality from 2015 are listed below.  The rankings are much more stable over time than they were for the employment dataset as most neighborhoods only increasing or decreasing in the single digits over the 14 year timespan.\footnote{Graphs for this section are also included in the Appendix.}\\

{\centering
\begin{figure}[H]
    \centering
    \includegraphics[width=0.75\textwidth]{Houses-S000-2015}
    \caption{This map shows the eigenvector that corresponds to the principal eigenvalue in 2015.}
    \label{fig:Houses-S000-2015}
\end{figure} } \\

\begin{table}[h]\centering
\caption{Housing Neighborhood Rank}\label{thelabel}

\begin{adjustbox}{center}
\begin{tabular}{||c | c c c c c c c c c c c c c c | c ||} 
 \hline
 & 2002 & 2003 & 2004 & 2005 & 2006 & 2007 & 2008 & 2009 & 2010 & 2011 & 2012 & 2013 & 2014 & 2015 & | \%\\[0.5ex] 
 \hline\hline
Logan Square & .303 & .307 & .307 & .296 & .287 & .207 & .296 & .201 & .313 & .316 & .323 & .333 & .340 & .322 & 6.27\% \\
West Rogers Park & .220 & .221 & .221 & .224 & .230 & .201 & .221 & .209 & .246 & .260 & .261 & .254 & .245 & .239 & 8.64\% \\
Gresham & .238 & .239 & .239 & .233 & .231 & .245 & .242 & .254 & .202 & .205 & .213 & .193 & .201 & .215 & -9.66\% \\
Portage Park & .188 & .185 & .185 & .181 & .182 & .214 & .191 & .220 & .201 & .203 & .190 & .198 & .188 & .189 & .53\% \\
Archer Heights & .181 & .178 & .178 & .186 & .182 & .187 & .173 & .185 & .198 & .173 & .175 & .184 & .186 & .188 & 3.87\% \\
Little Village & .208 & .200 & .200 & .196 & .193 & .201 & .176 & .201 & .178 & .171 & .183 & .187 & .197 & .188 & -9.62\% \\
Albany Park & .189 & .195 & .195 & .179 & .172 & .144 & .181 & .133 & .186 & .198 & .201 & .193 & .183 & .179 & -5.29\% \\
Englewood & .247 & .244 & .244 & .236 & .239 & .258 & .223 & .252 & .197 & .185 & .178 & .172 & .177 & .179 & -27.53\% \\
Bridgeport & .139 & .147 & .147 & .146 & .157 & .171 & .165 & .181 & .189 & .171 & .176 & .175 & .171 & .174 & 25.18\% \\
Rogers Park & .154 & .151 & .151 & .150 & .159 & .133 & .155 & .127 & .158 & .172 & .175 & .177 & .175 & .174 & 12.99\% \\ \hline
 \end{tabular}
\end{adjustbox}
\end{table}

@@

\begin{table}[h]\centering
\caption{Housing Neighborhood Rank - Age $<$ 29}\label{thelabel}
\begin{adjustbox}{center}
\begin{tabular}{||c | c c c c c c c c c c c c c c | c ||} 
 \hline
 & 2002 & 2003 & 2004 & 2005 & 2006 & 2007 & 2008 & 2009 & 2010 & 2011 & 2012 & 2013 & 2014 & 2015 & | \%\\[0.5ex] 
 \hline\hline
Logan Square & .355 & .364 & .341 & .353 & .338 & .262 & .368 & .235 & .388 & .385 & .398 & .408 & .391 & .385 & 8.45\% \\
Little Village & .248 & .247 & .244 & .253 & .234 & .235 & .200 & .228 & .207 & .202 & .224 & .224 & .230 & .217 & -12.50\% \\
Gresham & .194 & .201 & .215 & .197 & .190 & .209 & .219 & .227 & .164 & .173 & .174 & .158 & .187 & .209 & 7.73\% \\
Englewood & .244 & .257 & .253 & .239 & .234 & .262 & .226 & .254 & .183 & .157 & .165 & .162 & .175 & .205 & -15.98\% \\
Archer Heights & .197 & .184 & .191 & .199 & .191 & .198 & .174 & .205 & .209 & .166 & .186 & .195 & .198 & .189 & -4.06\% \\
Lake View & .155 & .171 & .191 & .185 & .212 & .186 & .214 & .156 & .240 & .215 & .208 & .191 & .177 & .187 & 2.65\% \\
Brighton Park & .187 & .189 & .182 & .186 & .189 & .145 & .158 & .145 & .156 & .164 & .159 & .183 & .170 & .179 & -4.28\% \\
West Rogers Park & .169 & .165 & .168 & .176 & .169 & .169 & .178 & .185 & .192 & .206 & .208 & .191 & .175 & .178 & 5.33\% \\
Rogers Park & .142 & .139 & .140 & .144 & .153 & .126 & .145 & .135 & .154 & .166 & .154 & .154 & .158 & .174 & 22.54\% \\
Marquette Park & .140 & .144 & .150 & .176 & .180 & .164 & .151 & .160 & .131 & .132 & .135 & .124 & .142 & .167 & 19.29\% \\
 \hline
 \end{tabular}

@@

\begin{table}[h]\centering
\caption{Housing Neighborhood Rank - Age over 55}\label{thelabel}
\begin{adjustbox}{center}
\begin{tabular}{||c | c c c c c c c c c c c c c c | c ||} 
 \hline
 & 2002 & 2003 & 2004 & 2005 & 2006 & 2007 & 2008 & 2009 & 2010 & 2011 & 2012 & 2013 & 2014 & 2015 & | \%\\[0.5ex] 
 \hline\hline
West Rogers Park & .229 & .248 & .234 & .220 & .225 & .186 & .247 & .183 & .273 & .293 & .301 & .302 & .273 & .281 & 22.71\% \\
Logan Square & .231 & .224 & .223 & .201 & .211 & .129 & .196 & .167 & .234 & .225 & .240 & .246 & .265 & .239 & 3.46\% \\
Portage Park & .183 & .202 & .213 & .204 & .189 & .220 & .219 & .239 & .216 & .240 & .225 & .215 & .242 & .235 & 28.42\% \\
Gresham & .314 & .292 & .319 & .312 & .301 & .280 & .261 & .283 & .238 & .238 & .221 & .220 & .228 & .229 & -27.07\% \\
Jefferson Park & .193 & .200 & .185 & .194 & .184 & .189 & .225 & .194 & .231 & .208 & .204 & .214 & .235 & .208 & 7.77\% \\
Bridgeport & .119 & .139 & .148 & .134 & .151 & .189 & .170 & .190 & .200 & .185 & .191 & .209 & .197 & .194 & 63.03\% \\
Albany Park & .155 & .164 & .159 & .164 & .150 & .118 & .176 & .121 & .174 & .179 & .192 & .182 & .175 & .186 & 2.00\% \\
Archer Heights & .159 & .156 & .155 & .181 & .173 & .178 & .168 & .167 & .194 & .160 & .163 & .172 & .158 & .168 & 5.66\% \\
Little Village & .150 & .154 & .164 & .162 & .169 & .181 & .150 & .196 & .155 & .145 & .167 & .163 & .171 & .161 & 7.33\% \\
West Pullman & .185 & .205 & .189 & .177 & .241 & .172 & .175 & .179 & .164 & .153 & .142 & .138 & .142 & .161 & -12.97\% \\
 \hline
 \end{tabular}
